Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-07-01 Manuscript.Rmd
B&B edits ready. NeuroImage version

The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017]. We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects. In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC. We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas. For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas. In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.

The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8. Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g. network B in right PCC of 100307). Even so, this result supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.

@@

```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (recreated based on descriptions from Braga et al. (2019)) and SP communities for two individuals. Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders. Correlation values are thresholded at 0.2. Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either DN sub-network."}

>>>>

The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017]. We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects. In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC. We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas. For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas. In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively. The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8. It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g. network B in right PCC of 100307).

Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. This result supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.

@@

```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al. (2019)) and SP communities for two individuals. Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders. Correlation values are thresholded at 0.2. Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A. The non-DN community covers sections of cortex not associated with either DN sub-network."}
